Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-07-24 manuscript/manuscript.tex
small change in the code availability section

The current version of our code is freely distributed under the
BSD 3-clause licence and it is available for at 
Zenodo (\url{http://doi.org/10.5281/zenodo.825261}). The latest
development version of our code can be freely downloaded from
a repository on GitHub (\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
Instructions for running the current version of our code
are also provided on the repository.
The code is still being improved and we encourage the user to 
work with the latest development version.
The code was developed as part of the Fatiando a Terra
\citep{uieda2013} open-source Python
library for modelling and inversion in geophysics.
Documentation and installation instructions for
the 0.5 release version of Fatiando a Terra
are provided at \url{http://www.fatiando.org/v0.5}.

>>>>

The current version of our code is freely distributed under the
BSD 3-clause licence and it is available for download at 
Zenodo (\url{http://doi.org/10.5281/zenodo.825261}). The latest
development version of our code can be freely downloaded from
a repository on GitHub (\url{https://github.com/pinga-lab/magnetic-ellipsoid}).
Instructions for running the current version of our code
are also provided on the repository.
The code is still being improved and we encourage the user to 
work with the latest development version.
The code was developed as part of the Fatiando a Terra
\citep{uieda2013} open-source Python
library for modelling and inversion in geophysics.
Documentation and installation instructions for
the 0.5 release version of Fatiando a Terra
are provided at \url{http://www.fatiando.org/v0.5}.
